|

### 2020-05-20 paper.Rmd
Additional references added.

- linear projections and tours [@As85,@BCAH05]
- most projections are approximately gaussian, as dimensionality increases, observations pile in the center [@diaconis1984]
- related: crowding problem as addressed in t-SNE [@tsne], data piling [XXX]
- regularisation?

>>>>

- linear projections and tours [@As85,@BCAH05]: we want to discover features, by looking at the data from all sides
- most projections are approximately gaussian, as dimensionality increases, observations pile in the center [@diaconis1984]
- related: crowding problem as addressed in t-SNE [@tsne]
- connection with high-dimension low-sample data? observations will be away from the center, on the vertices of a simples [@doi:10.1111/j.1467-9868.2005.00510.x], and we can find directions where data is piling in a single point [@10.2307/27639976,@10.1093/biomet/asp084]
- connection with regularisation? (optimisation vs visualisation)
